Generalized Universe Hierarchies and First-Class Universe Levels

### 2021-02-22 paper.tex
typo

Predicative hierarchies originate as Russell's ramified type theories
\cite{principia}. In the more modern formulations of type theory, Martin-Löf
proposed a countable predicative hierarchy \cite{martinlof73predicative}, as a
way to remedy the inconsistency of the previous version of the theory (which
assumed type-in-type). Harper and Pollack described universe inference with
level assignments and also a form of level polymorphism \cite{harperpollack}.
Sterling \cite{sterling2019algebraic} gave an algebraic specification much like
ours for a type theory with countable cumulative universes, and prove canonicity
for it.

@@

The answer is that IR provides is a \emph{deep embedding} of universe features,
which is usually less convenient to use as \emph{native} features. For example,
both Coq and Agda have powerful automatic solving for filling out implicit
universe levels. We also do not have to invoke $\El$ or the $\ult$ computation
rule explicitly, and in Coq we can use implicit syntax for subtyping instead of
explicit coercions.

>>>>

Predicative hierarchies originate from Russell's ramified type theories
\cite{principia}. In the more modern formulations of type theory, Martin-Löf
proposed a countable predicative hierarchy \cite{martinlof73predicative}, as a
way to remedy the inconsistency of the previous version of the theory (which
assumed type-in-type). Harper and Pollack described universe inference with
level assignments and also a form of level polymorphism \cite{harperpollack}.
Sterling \cite{sterling2019algebraic} gave an algebraic specification much like
ours for a type theory with countable cumulative universes, and prove canonicity
for it.

@@

The answer is that IR provides is a \emph{deep embedding} of universe features,
which is usually less convenient to use than \emph{native} features. For example,
both Coq and Agda have powerful automatic solving for filling out implicit
universe levels. We also do not have to invoke $\El$ or the $\ult$ computation
rule explicitly, and in Coq we can use implicit syntax for subtyping instead of
explicit coercions.
